---
title: "p8105_hw6_yw3608"
author: "Yuxuan Wang"
date: "12/2/2021"
output: github_document
---
# Problem 1
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(mgcv)
library(modelr)


```


**Prepare data,and check if missing data exist and drop na**
```{r,warning=FALSE,message = FALSE}
bw_df = 
  read_csv('data/birthweight.csv') %>% 
  drop_na()
```


**clean data, mutate several variables to factors,change level's name and show the data**
```{r}
bw_clean = 
  bw_df %>% 
  mutate(
    babysex = as.factor(babysex),
    father_race = as.factor(frace),
    malform = as.factor(malform),
    mother_race = as.factor(mrace)
  )  %>%
  mutate(
    babysex = recode(babysex, "1" = "male", "2" = "female"),
    father_race = recode(father_race, "1" = "white", "2" = "black", "3" = "asian", "4" = "puertorican", "8" = "other", "9" = "unknown"), 
    malform = recode(malform, "0" = "absense", "1" = "present"),
    mother_race = recode(mother_race, "1" = "white", "2" = "black", "3" = "asian", "4" = "puertorican", "8" =   "other")
    ) 
 
head(bw_clean) %>% 
knitr::kable()
```



**regression model**
```{r}
 model1 = lm(bwt ~ wtgain * ppwt, data = bw_clean)
  summary(model1) %>% 
  broom::tidy()
  
  
  
  bw_df %>% 
  modelr::add_predictions(model1) %>%
  modelr::add_residuals(model1) %>%
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = 0.6) 
```

**prepare the other two required models**
```{r}
model2 = lm(bwt ~ blength + gaweeks, data = bw_clean)
model3 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = bw_clean)

summary(model2) %>% 
  broom::tidy()

summary(model3) %>% 
  broom::tidy()
```



Compare the model to two other models:
model2:length at birth and gestational age as predictors (main effects only)
model3:head circumference, length, sex, and all interactions (including the three-way interaction) between these
```{r}
  cvpe_df = 
  crossv_mc(bw_clean, 100) %>% 
   mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  ) %>% 
  mutate(
    model1 = map(train, ~ lm(bwt~ wtgain * ppwt, data =.x )),
    model2 = map(train, ~ lm(bwt ~ blength + gaweeks, data = .x)),
    model3 = map(train, ~ lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex +       blength*babysex + bhead*blength*babysex, data = .x))) %>%
  
  mutate(
    rmse_model1 = map2_dbl(model1, test, ~rmse(model = .x, data = .y)),
    rmse_model2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y)),
    rmse_model3 = map2_dbl(model3, test, ~rmse(model = .x, data = .y)))

cvpe_df %>% 
  select(starts_with('rmse')) %>% 
  pivot_longer(
    rmse_model1:rmse_model3,
    names_to = 'model',
    values_to = 'rmse', 
    names_prefix = 'rmse_'
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
   geom_boxplot()


```




# Pproblem2**
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

